one target

### 2018-08-24 E2/analysis/histsWithFitsOneTarget.Rmd
right

```{r investigateDifficultyCollapsing}
#see preservingNonNumericWhenSummarizing.R
tw<- as_tibble(twoTarget)
tw<- tw %>% select(-targetStreamOrientations,-warnings,-letterSeq)
ty<- tw %>% group_by(subject,stream,orientation) %>% summarise_all(funs(if_else(is.numeric(.), mean(.), first(.))))

tt<- as_tibble(twoTarget) 
zb<- tt %>% group_by(subject,stream,orientation) %>% select(-targetStreamOrientations,-letterSeq) %>%
  summarise_all( function(x){ if(is.numeric(x)){ return(mean(x)) } else{ nth(x,-1) } })

#The below works, but remember I've eliminated the list and string columns
#zz<- tw %>% group_by(subject,stream,orientation) %>%
#  summarise_all(function(x){ifelse(is.numeric(x),mean(x),last(x))})

tt<- as_tibble(twoTarget)
za<- tt %>% group_by(subject,stream,orientation) %>%
  summarise_all(function(x){ifelse(is.numeric(x),mean(x),last(x))})

tz<-tw
tz$targetSide <- as.factor(tz$targetSide)
tz %>% group_by(subject,stream,orientation) %>% summarise_all(funs(if_else(is.numeric(.), mean(.), first(.))))

tw %>% group_by(subject,stream,orientation) %>% summarise_at("targetSide",first)

ty<- tw %>% group_by(subject,stream,orientation) %>% summarise_all(funs(if_else(is.numeric(.), mean(.), -999.9)))
```

@@

I suppose there are 4 one-target conditions also, upright/reversed x left/right
```{r }
#Calculate exclusions based on one-target performance
#oneTarget<- dg %>% filter(targetSide!="Both")
one<- oneTarget %>% group_by(subject,targetSide,orientation) %>% 
  select(-targetStreamOrientations,-letterSeq) %>% #can't include list columns
  select(-trial,-targetSP,-respSP,-respOrder) %>% #clear detritus so easier to see
  summarise_all( function(x){ if(is.numeric(x)){ return(mean(x)) } else{ nth(x,-1) } })

#Should probably look at the difference in efficacy between the left and the right
one %>% group_by(subject,targetSide) %>%   function(x) { x$effDiff = x %>% filter(stream=="Left")   -    x %>% filter(stream=="Right") }

one %>% group_by(subject,targetSide) %>% summarise_at("efficacy",
       function(x) { x %>% filter(stream=="Left")   -    x %>% filter(stream=="Right") }  )

  mutate(effDiff = 
       function(x) { x %>% filter(stream=="Left")$efficacy   -    x %>% filter(stream=="Right")$efficacy }  )

  summarise(LRtestFails = sum(pLRtest>.05), effFails = sum(efficacy<.1))

>>>>

@@

There are 4 one-target conditions also, upright/reversed x left/right.
Will exclude subject if failed likelihood test for both left and right in either condition.

Will also exclude if difference in efficacy left-right exceeds?
```{r }
#Calculate exclusions based on one-target performance
#oneTarget<- dg %>% filter(targetSide!="Both")
one<- oneTarget %>% group_by(subject,targetSide,orientation) %>% 
  select(-targetStreamOrientations,-letterSeq) %>% #can't include list columns
  select(-trial,-targetSP,-respSP,-respOrder) %>% #clear detritus so easier to see
  summarise_all( function(x){ if(is.numeric(x)){ return(mean(x)) } else{ nth(x,-1) } })

#Look at the difference in efficacy between the left and the right
effDiff <- function(df) {
  #dgi<<-df
  #STOP
  effLeft<- (df %>% filter(targetSide=="Left"))$efficacy 
  effRight<- (df %>% filter(targetSide=="Right"))$efficacy
  df$effDiff<- effLeft - effRight
  df$efficacy<- mean(c(effLeft,effRight))
  df$effDiff<- effLeft - effRight

  failedBothLR <- ((df %>% filter(targetSide=="Left"))$pLRtest >= .05) &
    ((df %>% filter(targetSide=="Right"))$pLRtest >= .05)
  df$failedBothLR <- failedBothLR

  return(df[1,]) #return first row, so it does get collapsed
}

oneDiff<- one %>% group_by(subject,orientation) %>% do( effDiff(.) )
oneDiff<- oneDiff %>% select(subject,targetSide,orientation,efficacy,effDiff,pLRtest,failedBothLR)
oneDiff

oneTargetLosers <- oneDiff %>% filter(failedBothLR == TRUE, effDiff > .4)

Make scatterplot of efficacy for left vs. right single target

```{r}
#To do that, do I need to unmelt?
ggplot(one, aes(x=
```

Make scatterplot of efficacy difference between left and right single target on horizontal axis and dual-target difference on vertical axis.

```{r}
